---
title: "USC Predict COVID Project"
subtitle: "Predictive Epidemic Model for COVID-19 in Los Angeles County"
author: "University of Southern California, Department of Preventive Medicine"
output:
  html_document:
    css: "styles.css"
    toc: true
    toc_depth: 2
    toc_float: true
editor_options: 
  chunk_output_type: console
---

<!--
NOTES:
- All data is read-in in the index.Rmd file
- All code is sourced in the index.Rmd file?

-->

<!--Initialize-->

``` {r setup, include=FALSE}

### Install necessary packages and get started

library(reshape2)
library(tidyverse)
library(ggplot2)
library(plotly)
library(ggrepel)
library(bindata)
library(odin)
library(fitR)
library(knitr)
library(EasyABC)
library(gridExtra)
library(odin)
library(lubridate)
library(EasyABC)
library(gridExtra)
library(kableExtra)
library(plyr)
library(dplyr)
library(data.table)
library(scales)
library(EasyABC)
library(patchwork)

library(tidyr)
library(readr)
library(purrr)
library(tibble)
library(stringr)
library(forcats)
library(network)
library(tidygraph)
library(ggraph)
library(visNetwork)
library(networkD3)
library(ggmosaic)
library(formattable)
library(DT)
library(reshape)
library(here)
library(fs)

library(MASS)
library(plotly)

lang_output <- function(x, lang) {
  cat(c(sprintf("```%s", lang), x, "```"), sep = "\n")
}
r_output <- function(x) lang_output(x, "r")

knitr::opts_chunk$set(
  fig.width = 9.5,
  fig.height = 8,
  eval=TRUE,
  echo=FALSE,
  warning=FALSE,
  cache=FALSE,
  message=FALSE,
  include=TRUE
  )

code.dir=here("code/")
data.dir=here("data/")
result.dir = here("results/")
fig.dir = here("figs/")
output.dir = here("output/")
code.paper.dir=here("code/")
code.risk.dir=here("code/risk_model_code/")
code.scenarios.dir=here("code/scenarios_code/")
```

<!--Set options-->

```{r options, include=FALSE}
print.output <- FALSE
days.truncate <- 15
```


<!--Read in epidemic model, functions, COVID data-->

```{r read-in-model-supporting-functions, include=FALSE}

###################################################################################################
## LOAD EPIDEMIC MODEL
## And compile the model
path_seihqdr_model <- path(code.paper.dir, "stochastic_SEIAHQDR_Alphat_rt.R")
seihqdr_generator <- odin::odin(path_seihqdr_model)

###################################################################################################
## LOAD DATA PROCESSING AND MODEL ESTIMATING FUNCTIONS
model_functions <- path(code.paper.dir, "data_model_fun.R")
r_output(tail(readLines(model_functions)))
source(model_functions)

###################################################################################################
## LOAD PLOTTING FUNCTIONS
plot_code <- path(code.paper.dir, "plotting_fun.R")
source(plot_code)

###################################################################################################
## LOAD TABLES FUNCTIONS
tables_code <- path(code.paper.dir, "tables_fun.R")
source(tables_code)

###################################################################################################
## COVID INPUT DATA
# latest_data: cumulative and daily counts for "Htotcum","D","Vcum","Idetectcum","H_new","D_new"
# no_obs: number of observation days
latest_data <- latest_covid_data(truncate=days.truncate)
no_obs <- nrow(latest_data)

```


<!--Model Fitting-->

```{r include=FALSE}

## SOURCE PRIOR PARAMETERS
## Provides output in form of a prior.par list
## Note: Beta(t), Alpha(t), Kappa(t), Delta(t) are read in from file
prior_param_input <- path(code.paper.dir, "prior_param.R")
source(prior_param_input)
# prior.par

## SUMMARY STATISTICS COMPUTED ON DATA
summarydata <- sum.stats.SIMTEST(latest_data,include.R = FALSE)
model.R <- model.1sim.stats.no.R  # From supporting_functions

### NUMBER OF OUTPUTS
# n_calibration = 10000
# n_rec = 2000

n_calibration = 1000
n_rec = 100

## FIT MODEL
ABC_out<-ABC_mcmc(method="Marjoram",model=model.R,prior=prior.par,
                       summary_stat_target=summarydata, n_calibration=n_calibration,
                       tolerance_quantile=0.1,verbose=FALSE,progress=TRUE, n_rec=n_rec)

ABC.par.out <- as.data.frame(ABC_out$param)
ABC.out.mat <- ABC_out$param
par.vec.length <- nrow(ABC_out$param)

```

<!--DON'T INCLUDE-->

```{r EASYRUN, eval=FALSE, include=FALSE}
#########################################################
#########################################################
#########################################################
## FUNCTION MODEL.OUTPUT.TO.PLOT.SIM
## Calculates mean and CI of each estimated parameter & CFR/IFR
## Uses correlated.param.SIM
## Reads in Beta(t), Alpha(t), Kappa(t), Delta(t) from file
iter <- 10
time.steps <- 400
vars.to.plot <- vars.plus.R
traj.0 <- model.output.to.plot.SIM(ABC.out.mat=ABC.out.mat, par.vec.length=par.vec.length, iter=iter, time.steps=time.steps, vars.to.plot = vars.to.plot)

## FUNCTION PLOT.ALL.VARIABLES
time.steps.4.plot = as.Date("2020-11-15") - as.Date("2020-03-01") + 1
data.in <- latest_data
vars.to.plot <- vars.plus.R

plot.all.variables <- 
plot.model.data.all(traj.CI = traj.0, data.in = data.in, init.date.data = "2020-03-01", date.offset.4plot = 15, time.steps.4plot=time.steps.4.plot,
                    vars.to.plot=vars.plus.R)
plot.all.variables
```

<!--DON'T INCLUDE-->

```{r EASYRUN_CONTINUED, eval=FALSE, include=FALSE}

date.in <- seq(as.Date("2020-03-01"), as.Date("2020-11-01"), by="2 weeks")

CFR.IFR.plots.out <- CFR.IFR.plots(traj.CI=traj.0, date.in=date.in)
CFR.plot <- CFR.IFR.plots.out[[1]]
IFR.plot <- CFR.IFR.plots.out[[2]]
CFR.plot+IFR.plot

tables.out <- summary.table.param.CFR.IFR(traj.CI=traj.0, ABC_out=ABC_out, date.in=date.in, use.mean.select = 1, round.by.in = 4)
table.epi <- tables.out[[1]]
table.epi
tables.out[[2]]
tables.out[[3]]
#plot.all.variables

Fig3.plots <- plot.param.t(ABC_out = ABC_out)
Fig3.plots[[3]]
Fig3.plots[[1]]


var.to.plot <- "I"
yesR.p.I.0 <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01", date.offset.4plot=0, 
                           time.steps.4plot=time.steps.4.plot, ymax=50000, plot.capacity=NULL, var.to.plot=var.to.plot,use.title=NULL,
                           scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux)
ggplotly(yesR.p.I.0)

var.to.plot <- "Htot"
yesR.p.I.0 <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01", date.offset.4plot=0, 
                           time.steps.4plot=time.steps.4.plot, ymax=3000, plot.capacity=TRUE, var.to.plot=var.to.plot,use.title=NULL,
                           scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux)
ggplotly(yesR.p.I.0)


```


<!--Simulate model-->
<!--Get compartment variables over time with CI-->
<!--Get CFR/IFR-->

```{r include=FALSE}
###################################################################################################
## GET MODEL OUTPUT: traj.0

ABC.out.mat <- ABC_out$param
par.vec.length <- nrow(ABC_out$param)
iter <- 10
time.steps <- 400
vars.to.plot <- vars.plus.R

## FUNCTION MODEL.OUTPUT.TO.PLOT.SIM
## Calculates mean and CI of each estimated parameter & CFR/IFR
## Uses correlated.param.SIM
## Reads in Beta, Alpha, Kappa, Delta from file
traj.0 <- model.output.to.plot.SIM(ABC.out.mat=ABC.out.mat, par.vec.length=par.vec.length, iter=iter, time.steps=time.steps, vars.to.plot = vars.to.plot)

```

# Epidemic model

## Tables: Parameter estimates {.tabset}

```{r include=FALSE}
###################################################################################################
## GET MODEL OUTPUT: summary

date.in <- seq(as.Date("2020-03-01"), as.Date("2020-11-01"), by="2 weeks")
tables.out <- summary.table.param.CFR.IFR(traj.CI=traj.0, ABC_out=ABC_out, date.in=date.in, use.mean.select = 1, round.by.in=4)

```

### $R0$, $r(t)$, $\mu(t)$
```{r}
formattable(tables.out[[1]])
if (print.output==TRUE) write.csv(tables.out[[1]], file = path(output.dir, "R.r.mu_table.csv"))
```

### $\alpha(t)$, $\kappa(t)$, $\delta(t)$

```{r}
formattable(tables.out[[2]])
akd_table <- tables.out[[2]]
if (print.output==TRUE) write.csv(tables.out[[2]], file = path(output.dir, "AKD_t_table.csv"))
```

### CFR and IFR

```{r}
formattable(tables.out[[3]])
if (print.output==TRUE) write.csv(tables.out[[3]], file = path(output.dir, "CFR_IFR_table.csv"))
```

## Figure: Model fits

Summarizes the epidemic model fit with COVID-19 data for LAC from March 1 through `r as.Date("2020-03-01") + no_obs` for all disease states across multiple views: New cases, representing new daily incidence; the current number in a compartment at a specific date, relevant for understanding current prevalence rates and comparing with healthcare capacity limitations; and cumulative counts until a specific date. Observed data for available compartments with cases attributable to nursing home residents removed, are plotted as black dots. The figure demonstrates that good model fits are achieved in all compartments across time.

* **New = new daily incidence**
* **Current = current census in compartment** 
* **Cumulative = running total over time**
* Black dots depict COVID-19 data, with counts from outbreaks in nursing homes removed
* The dashed line represents healthcare resource capacity limits

```{r include=FALSE}

###################################################################################################
## Plot all variables faceted

time.steps.4.plot = as.Date("2020-11-15") - as.Date("2020-03-01") + 1
data.in <- latest_data
vars.to.plot <- vars.plus.R

plot.all.variables <- 
plot.model.data.all(traj.CI = traj.0, data.in = data.in, init.date.data = "2020-03-01", date.offset.4plot = 15, time.steps.4plot=time.steps.4.plot,
                    vars.to.plot=vars.plus.R)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot.all.variables.pdf"), width=10, height =10)
  plot.all.variables
  dev.off()
}

```

```{r}
plot.all.variables
```


## Figures: Time-Varying Parameters {.tabset}

```{r include=FALSE}

endDatePlot <- as.Date("2020-12-01")
Fig3.plots <- plot.param.t(ABC_out = ABC_out, endDatePlot=endDatePlot)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot_R_t.pdf"), width=10, height =10)
  Fig3.plots[[1]]
  dev.off()
  
  pdf(file = path(output.dir, "plot_r_t.pdf"), width=10, height =10)
  Fig3.plots[[2]]
  dev.off()
  
  pdf(file = path(output.dir, "plot_AKD_t.pdf"), width=10, height =10)
  Fig3.plots[[3]]
  dev.off()
}

```

### Reproductive Number $R(t)$

```{r}
Fig3.plots[[1]]
```

### Fraction of Observed Infections $r(t)$

```{r}
Fig3.plots[[2]]
```

### $\alpha(t)$, $\kappa(t)$, $\delta(t)$

```{r}
Fig3.plots[[3]]
```

<!--CFR and IFR-->

```{r include=FALSE}

date.in <- seq(as.Date("2020-03-01"), as.Date("2020-11-01"), by="2 weeks")
endDatePlot <- as.Date("2020-12-01")
CFR.IFR.plots.out <- CFR.IFR.plots(traj.CI=traj.0, date.in=date.in)

if (print.output==TRUE){
  pdf(file = path(output.dir, "CFR_plot.pdf"), width=10, height =10)
  CFR.IFR.plots.out[[1]]
  dev.off()
  
  pdf(file = path(output.dir, "IFR_plot.pdf"), width=10, height =10)
  CFR.IFR.plots.out[[2]]
  dev.off()
}
```

### Time-varying CFR(t)

```{r}
CFR.IFR.plots.out[[1]]
```

### Time-varying IFR(t)
```{r}
CFR.IFR.plots.out[[2]]
```



# Risk model

```{r setup-print-formattable}

library("htmltools")
library("webshot")    

# FOR PRINTING LONG WITH ALL COLUMNS
# export_formattable <- function(f, file, width = "100%", height = "70%",#,
#                                background = "white", delay = 0.2)

# FOR PRINTING CONDENSED (LOOKS BETTER)
export_formattable <- function(f, file, width = "110%", height = NULL,#, 
                               background = "white", delay = 0.2)
    {
      w <- as.htmlwidget(f, width = width, height = height)
      path <- html_print(w, background = background, viewer = NULL)
      url <- paste0("file:///", gsub("\\\\", "/", normalizePath(path)))
      webshot(url,
              file = file,
              selector = ".formattable_widget",
              delay = delay)
}

## TRY: as.htmlwidget.formattable
## TRY: px *	pixels (1px = 1/96th of 1in)
## SEE: https://www.w3schools.com/cssref/tryit.asp?filename=trycss_dim_width

```

# Risk model

<!--- 
Read in data
--->

```{r include=FALSE}
###############################################################################################################
## Read in marginal risk probability P(H|I), P(Q|H), P(D|Q) for each risk profile q, calculated by the JAM model
## Data coming from: Guan et al. 2020, Petrilli et al. 2020
Pr.H <- read.csv(path(data.dir, "Pr.H.csv"), sep=",", header=TRUE,row.names = 1)
Pr.Q <- read.csv(path(data.dir, "Pr.Q.csv"), sep=",", header=TRUE,row.names = 1)
Pr.D <- read.csv(path(data.dir, "Pr.D.csv"), sep=",", header=TRUE,row.names = 1)

## Get profile matrix X.mat
X.mat <- as.matrix(dplyr::select(Pr.H, -1))
n_factors <- ncol(X.mat)
n_profiles <- nrow(X.mat)

#########################################################################################################
## Read in prevalence of each risk factor p in the population for LA County
## Data coming from:
#### [Los Angeles County Health Survey](http://www.publichealth.lacounty.gov/ha/hasurveyintro.htm)
#### [California Health Information Survey](http://ask.chis.ucla.edu)
Pop.prevalence <- read.csv(path(data.dir, "Pop.prevalence.LA.csv"), sep=",", header=TRUE,row.names = 1 )
Pop.prev.matrix<-as.matrix(Pop.prevalence)

#########################################################################################################
## Read in correlation structure, $\Sigma$, between the risk factors p
## Correlation structure is weighted according to the prevalence of each race/ethnicity in LA County
## Calculated using data coming from: The National Health and Nutrition Examination Survey (NHANES)
SIGMA <- read.csv(path(data.dir, "SIGMA.csv"), sep=",", header=TRUE,row.names = 1)

```

<!---
Calculate prevalence of each profile in overall LAC population
--->

```{r riskprofiles, include=FALSE, eval=TRUE}
calc_profile_prev<- path(code.risk.dir, "calc_profile_prev.R")
r_output(readLines(calc_profile_prev))
source(calc_profile_prev)

## OUTPUT
# profile.cnt.freq
```

<!---
Estimate risk probabilities with baseline from epidemic model
--->

```{r estimate-risk-integrated}

##################################################
## INPUTS: TIMES
### Chosen times to run analysis at
# t1 <- "2020-04-15"
# t2 <- "2020-07-15"
# t3 <- "2020-10-15"
# table.dates <- c("Apr.15","Jul.15","Oct.15")
# times <- c("t1", "t2", "t3")
# times.dates <- as.Date(c(t1,t2,t3))
t1 <- "2020-05-15"
t2 <- "2020-08-01"
t3 <- "2020-10-15"
table.dates <- c("May.15","Aug.1","Oct.15")
times <- c("t1", "t2", "t3")
times.dates <- as.Date(c(t1,t2,t3))
# t1 <- "2020-05-15"
# t2 <- "2020-07-15"
# t3 <- "2020-09-15"
# t4 <- "2020-10-15"
# table.dates <- c("May.15","Jul.15","Sep.15","Oct.15")
# times.dates <- as.Date(c(t1,t2,t3,t4))
# times <- c("t1","t2","t3","t4")
n.times <- length(times)

##################################################
## INPUTS: OBSERVED LAC DATA ON ILLNESSES
### Observed LAC age prevalence in (I) infections
n.dates.LAC.obs.age <- length(times)
freq.LAC.obs.age <- matrix(nrow=3, ncol=n.dates.LAC.obs.age)
colnames(freq.LAC.obs.age) <- times
rownames(freq.LAC.obs.age) <- c("Age0.19","Age20.64","Age65.")
# freq.LAC.obs.age[,1] <- c(0.011, 0.750, 0.239)  # Apr15
# freq.LAC.obs.age[,2] <- c(0.080, 0.799, 0.121)  # Jul15
# freq.LAC.obs.age[,3] <- c(0.102, 0.784, 0.114)  # Oct15
# freq.LAC.obs.age[,1] <- c(0.035, 0.749, 0.216)  # May15
# freq.LAC.obs.age[,2] <- c(0.080, 0.799, 0.121)  # Jul15
# freq.LAC.obs.age[,3] <- c(0.099, 0.785, 0.116)  # Sep15
# freq.LAC.obs.age[,4] <- c(0.102, 0.784, 0.114)  # Oct15
freq.LAC.obs.age[,1] <- c(0.035, 0.749, 0.216)  # May.15
freq.LAC.obs.age[,2] <- c(0.089, 0.791, 0.120)  # Aug.1
freq.LAC.obs.age[,3] <- c(0.102, 0.784, 0.114)  # Oct.15


##################################################
## INPUTS: EPIDEMIC MODEL
## Get mean estimates of Alpha(t), Kappa(t), Delta(t) at each time point 
akd_table <- tables.out[[2]]
table1 <- akd_table
for (i in 1:2){  table1[i,] <- akd_table[i,] %>% mutate_if(is.character, function(x) unlist(strsplit(x, " "))[1])}
table1 <- as.data.frame(apply(table1, 2, as.numeric)) 

## Create extra rows representing Alpha, Kappa, Delta values for t > 2 (with same values for Alpha, Kappa, Delta as t2)
if (n.times > 2){ for (exrow in 3:n.times) table1[exrow,] <- table1[2,] }
rownames(table1) <- times
risk.probs.POSTERIORS <- table1

##################################################
## INPUTS: PROFILE FREQUENCY
### Estimated frequency of each risk profile
freq.PREV.q <- as.vector(profile.cnt.freq[,1])

##################################################
## INPUTS: JAM ESTIMATED CONDITIONAL RISK EFFECTS
### Read in JAM produced conditional effect estimates
psi.mat = read.csv(path(data.dir, "psi.conditional.effect.estimates.csv"), sep=",", header=TRUE,row.names = 1)
rownames(psi.mat) <- colnames(X.mat)
psi.mat[1,] <- c(rep(-1,times=3))

##################################################
## APPLY CODE TO GET ESTIMATE RISK PROBABILITIES WITH BASELINE FROM EPIDEMIC MODEL
calc_integrated_risk_model<- path(code.risk.dir, "integrated_risk_model.R")
r_output(readLines(calc_integrated_risk_model))
source(calc_integrated_risk_model)

### OUTPUTS
Pr.OUT <- Pr.OUT
freq.OUT <- freq.OUT

```


```{r clean-data-get-CFR}

## INPUTS
#X.mat
#Pr.OUT
#freq.OUT

clean_data_risk_estimates_LAC <- path(code.risk.dir,"clean_data_integrated_risk.R")
r_output(readLines(clean_data_risk_estimates_LAC))
source(clean_data_risk_estimates_LAC)

## OUTPUTS
#data.prev #used for CFR/IFR calculation

## Note: The 5 risk groups are assigned within this code
##       Currently are grouped according to Pr(D|I).
##       To modify the risk grouping cutoffs see the end of this code.

```



```{r risk_table_ALL_COLUMNS_INCLUDED, include=FALSE}

ABC.out.mat <- ABC_out$param
time.steps = 400
iter <- 10
round.by <- 6
times.dates <- times.dates
# Requires data.prev from clean_data_risk_estimates_LAC

########################################################################
## risk.table.CFR.fn code found in clean_data_risk_estimates.R
########################################################################

risk_table_CFR_FULL <- risk.table.CFR.IFR.dates(ABC.out.mat=ABC.out.mat, time.steps=time.steps, iter=iter, data.prev=data.prev, times.dates=times.dates, round.by=round.by)

risk_table_CFR <- risk_table_CFR_FULL[,c("Profile","riskprofile","age","comorbidity","BMI","smoking","freq.PREV.q", paste0("freq.I.",times),            
                                    paste0("CFR.",times),paste0("IFR.",times))]
#vars <- c("freq.I.","CFR.","IFR.")
#apply(expand.grid(vars, times), 1, paste, collapse="")
#risk_table_CFR <- filter(risk_table_CFR, "I.prev.t1" > 0.000000004)  # FILTER PROFILES TO SHOW IN THE TABLE TO ONLY THOSE > 0 PREVALENCE
risk_table_CFR <- arrange(risk_table_CFR, desc(risk_table_CFR$"CFR.t1"))
risk_table_CFR <- risk_table_CFR %>% mutate_if(is.numeric, round, digits=4)
colnames(risk_table_CFR)[colnames(risk_table_CFR)=="freq.PREV.q"] <- "Pop.Prev"
colnames(risk_table_CFR)[colnames(risk_table_CFR)=="riskprofile"] <- "Group"
colnames(risk_table_CFR)[colnames(risk_table_CFR)==paste0("freq.I.",times)] <- paste0("Inf.",times.dates)
colnames(risk_table_CFR) <- c(colnames(risk_table_CFR)[1:7], paste0("Inf.",table.dates), paste0("CFR.",table.dates), paste0("IFR.",table.dates))
risk_table_CFR <- filter(risk_table_CFR, Pop.Prev > 0.00001)  # FILTER PROFILES TO SHOW IN THE TABLE TO ONLY THOSE > 0 PREVALENCE

unit.scale = function(x) (x - min(x)) / (max(x) - min(x))

risk_table_CFR.FT <- formattable(risk_table_CFR, align="c",
            #align = c(rep("c", 9)),
            list(
  `age`= color_tile('yellow', 'darkorange'),
  `BMI`= color_tile('lightblue', 'pink'),
  `smoking`= color_tile('grey', 'transparent'),
  `comorbidity`= color_tile('darkgrey', 'transparent'),
  `Group`= color_tile('red', 'green'),
  `Pop.Prev`= color_bar('cornflowerblue', fun = unit.scale),
    `Inf.May.15`= color_bar('orchid', fun = unit.scale),
  `Inf.Aug.1`= color_bar('plum', fun = unit.scale),
  `Inf.Oct.15`= color_bar('lightpink', fun = unit.scale),
  `CFR.May.15`= color_bar('orchid', fun = unit.scale),
  `CFR.Aug.1`= color_bar('plum', fun = unit.scale),
  `CFR.Oct.15`= color_bar('lightpink', fun = unit.scale),
  `IFR.May.15`= color_bar('orchid', fun = unit.scale),
  `IFR.Aug.1`= color_bar('plum', fun = unit.scale),
  `IFR.Oct.15`= color_bar('lightpink', fun = unit.scale)
))

pop_avg <- c("Pop-Avg", rep("",times=9), tables.out[[3]][c("2020-05-10", "2020-08-02","2020-10-11"),1], tables.out[[3]][c("2020-05-10", "2020-08-02","2020-10-11"),2])
names(pop_avg) <- colnames(risk_table_CFR.FT)
pop_avg <- as.data.frame(t(pop_avg))
formattable(pop_avg)
rbind(pop_avg, risk_table_CFR.FT)

(cbind(tables.out[[3]][c("2020-05-10", "2020-08-02","2020-10-11"),1], tables.out[[3]][c("2020-05-10", "2020-08-02","2020-10-11"),2]))

#export_formattable(risk_table_CFR.FT, path(output.dir,"TEST_CFRIFR.png"))

#risk_table_CFR.DT <- as.datatable(risk_table_CFR.FT, rownames = TRUE, options = list(pageLength = 10, autoWidth = TRUE))

```


```{r risk_table_FILTERED, include=FALSE}

ABC.out.mat <- ABC_out$param
time.steps = 400
iter <- 10
round.by <- 6
times.dates <- times.dates
# Requires data.prev from clean_data_risk_estimates_LAC

########################################################################
## risk.table.CFR.fn code found in clean_data_risk_estimates.R
########################################################################

risk_table_CFR_FULL <- risk.table.CFR.IFR.dates(ABC.out.mat=ABC.out.mat, time.steps=time.steps, iter=iter, data.prev=data.prev, times.dates=times.dates, round.by=round.by)

risk_table_CFR <- risk_table_CFR_FULL[,c("Profile","riskprofile","age","comorbidity","BMI","smoking","freq.PREV.q", paste0("freq.I.",times),            
                                    paste0("CFR.",times),paste0("IFR.",times))]
#vars <- c("freq.I.","CFR.","IFR.")
#apply(expand.grid(vars, times), 1, paste, collapse="")
#risk_table_CFR <- filter(risk_table_CFR, "I.prev.t1" > 0.000000004)  # FILTER PROFILES TO SHOW IN THE TABLE TO ONLY THOSE > 0 PREVALENCE
risk_table_CFR <- arrange(risk_table_CFR, desc(risk_table_CFR$"CFR.t1"))
risk_table_CFR <- risk_table_CFR %>% mutate_if(is.numeric, round, digits=4)
colnames(risk_table_CFR)[colnames(risk_table_CFR)=="freq.PREV.q"] <- "Pop.Prev"
colnames(risk_table_CFR)[colnames(risk_table_CFR)=="riskprofile"] <- "Group"
colnames(risk_table_CFR)[colnames(risk_table_CFR)==paste0("freq.I.",times)] <- paste0("Inf.",times.dates)
colnames(risk_table_CFR) <- c(colnames(risk_table_CFR)[1:7], paste0("Inf.",table.dates), paste0("CFR.",table.dates), paste0("IFR.",table.dates))
risk_table_CFR <- filter(risk_table_CFR, Pop.Prev > 0.0024)  # FILTER PROFILES TO SHOW IN THE TABLE TO ONLY THOSE > 0 PREVALENCE

unit.scale = function(x) (x - min(x)) / (max(x) - min(x))

risk_table_CFR.FT <- formattable(risk_table_CFR, align="c",
            #align = c(rep("c", 9)),
            list(
  `age`= color_tile('yellow', 'darkorange'),
  `BMI`= color_tile('lightblue', 'pink'),
  `smoking`= color_tile('grey', 'transparent'),
  `comorbidity`= color_tile('darkgrey', 'transparent'),
  `Group`= color_tile('red', 'green'),
  `Pop.Prev`= color_bar('cornflowerblue', fun = unit.scale),
    `Inf.May.15`= color_bar('orchid', fun = unit.scale),
  `Inf.Aug.1`= color_bar('plum', fun = unit.scale),
  `Inf.Oct.15`= color_bar('lightpink', fun = unit.scale),
  `CFR.May.15`= color_bar('orchid', fun = unit.scale),
  `CFR.Aug.1`= color_bar('plum', fun = unit.scale),
  `CFR.Oct.15`= color_bar('lightpink', fun = unit.scale),
  `IFR.May.15`= color_bar('orchid', fun = unit.scale),
  `IFR.Aug.1`= color_bar('plum', fun = unit.scale),
  `IFR.Oct.15`= color_bar('lightpink', fun = unit.scale)
))
risk_table_CFR.FT

pop_avg <- c("Pop-Avg", rep("",times=9), tables.out[[3]][c("2020-05-10", "2020-08-02","2020-10-11"),1], tables.out[[3]][c("2020-05-10", "2020-08-02","2020-10-11"),2])
names(pop_avg) <- colnames(risk_table_CFR.FT)
pop_avg <- as.data.frame(t(pop_avg))
formattable(pop_avg)
rbind(pop_avg, risk_table_CFR.FT)

(cbind(tables.out[[3]][c("2020-05-10", "2020-08-02","2020-10-11"),1], tables.out[[3]][c("2020-05-10", "2020-08-02","2020-10-11"),2]))

#export_formattable(risk_table_CFR.FT, path(output.dir,"TEST_CFRIFR.png"))

#risk_table_CFR.DT <- as.datatable(risk_table_CFR.FT, rownames = TRUE, options = list(pageLength = 10, autoWidth = TRUE))

```


## CFR and IFR table

```{r}
risk_table_CFR.FT
```

