---
title: "COVID19 Modeling for Los Angeles County"
subtitle: Analysis updated with data as of `r Sys.Date()`
author: "University of Southern California, Department of Preventive Medicine"
output:
  html_document:
    css: styles.css
    toc: yes
    toc_depth: 2
    toc_float: yes
editor_options:
  chunk_output_type: console
---

<br>
<br>
<br>

<!--Initialize-->

``` {r setup, include=FALSE}

### Install necessary packages and get started

library(reshape2)
library(tidyverse)
library(ggplot2)
library(plotly)
library(ggrepel)
library(bindata)
library(odin)
library(fitR)
library(knitr)
library(EasyABC)
library(gridExtra)
library(odin)
library(lubridate)
library(EasyABC)
library(gridExtra)
library(kableExtra)
library(plyr)
library(dplyr)
library(data.table)
library(scales)
library(EasyABC)
library(patchwork)

library(tidyr)
library(readr)
library(purrr)
library(tibble)
library(stringr)
library(forcats)
library(network)
library(tidygraph)
library(ggraph)
library(visNetwork)
library(networkD3)
library(ggmosaic)
library(formattable)
library(DT)
library(reshape)
library(here)
library(fs)

library(MASS)
library(plotly)

lang_output <- function(x, lang) {
  cat(c(sprintf("```%s", lang), x, "```"), sep = "\n")
}
r_output <- function(x) lang_output(x, "r")

knitr::opts_chunk$set(
  fig.width = 9.5,
  fig.height = 8,
  eval=TRUE,
  echo=FALSE,
  warning=FALSE,
  cache=FALSE,
  message=FALSE,
  include=TRUE
  )

code.dir=here("code/")
data.dir=here("data/")
data.update.dir=here("data/risk_update")
result.dir = here("results/")
fig.dir = here("figs/")
output.dir = here("output/")
output.density.dir = here("output/epi_model_output/density")
code.paper.dir=here("code/epi_model_code")
code.risk.dir=here("code/risk_model_code/2021")
code.scenarios.dir=here("code/scenarios_code/")
```

<!--Set global options-->

```{r options, include=FALSE}
print.output <- TRUE
days.truncate <- 0
endDatePlotGlobal <- as.Date("2021-03-01")
no_obs <- as.numeric(endDatePlotGlobal - as.Date("2020-03-01")) + 1
```


<!--Read in epidemic model, functions, COVID data-->

```{r read-in-model-supporting-functions, include=FALSE}

###################################################################################################
## LOAD EPIDEMIC MODEL
## And compile the model
path_seihqdr_model <- path(code.paper.dir, "stochastic_SEIAHQDR_Alphat_rt.R")
seihqdr_generator <- odin::odin(path_seihqdr_model)

###################################################################################################
## LOAD DATA PROCESSING AND MODEL ESTIMATING FUNCTIONS
model_functions <- path(code.paper.dir, "data_model_fun.R")
source(model_functions)

###################################################################################################
## LOAD PLOTTING FUNCTIONS
plot_code <- path(code.paper.dir, "plotting_fun_NEW.R")
source(plot_code)

###################################################################################################
## LOAD TABLES FUNCTIONS
tables_code <- path(code.paper.dir, "table_fun_NEW.R")
source(tables_code)

###################################################################################################
## COVID INPUT DATA
## latest_data: cumulative and daily counts for "Htotcum","D","Vcum","Idetectcum","H_new","D_new"
## no_obs: number of observation days

# latest_data <- latest_covid_data(truncate=days.truncate)
# no_obs <- nrow(latest_data)

latimes_path <- path(code.paper.dir, "LAtimes.R")
source(latimes_path)
la_data <- latimes_readin()

```


<!--Model Fitting-->

```{r model-fitting-code, include=FALSE}

## SOURCE PRIOR PARAMETERS
## Provides output in form of a prior.par list
## Note: Beta(t), Alpha(t), Kappa(t), Delta(t) are read in from file
prior_param_input <- path(code.paper.dir, "prior_param.R")
source(prior_param_input)
# prior.par

## SUMMARY STATISTICS COMPUTED ON DATA
#summarydata <- sum.stats.SIMTEST(latest_data,last_date_data = "2021-01-18") # function sum.stats.SIMTEST from supporting_functions
summarydata <- sum.stats.SIMTEST(la_data[c(1:no_obs),])
model.R <- model.1sim.stats.no.R  # From supporting_functions

### NUMBER OF OUTPUTS
n_calibration = 1000
n_rec = 100
# n_calibration = 10000
# n_rec = 2000

## FIT MODEL
ABC_out<-ABC_mcmc(method="Marjoram",model=model.R,prior=prior.par,
                       summary_stat_target=summarydata, n_calibration=n_calibration,
                       tolerance_quantile=0.1,verbose=FALSE,progress=TRUE, n_rec=n_rec)

ABC.par.out <- as.data.frame(ABC_out$param)
ABC.out.mat <- ABC_out$param
par.vec.length <- nrow(ABC_out$param)

```


<!--Simulate model-->
<!--Get compartment variables over time with CI-->
<!--Get CFR/IFR-->

```{r include=FALSE}
###################################################################################################
## GET MODEL OUTPUT: traj.0

ABC.out.mat <- ABC_out$param
par.vec.length <- nrow(ABC_out$param)
iter <- 10
time.steps <- 500
vars.to.plot <- vars.plus.R

## FUNCTION MODEL.OUTPUT.TO.PLOT.SIM
## Calculates mean and CI of each estimated parameter & CFR/IFR
## Uses correlated.param.SIM
## Reads in Beta, Alpha, Kappa, Delta from file
traj.0 <- model.output.to.plot.SIM(ABC.out.mat=ABC.out.mat, par.vec.length=par.vec.length, iter=iter, time.steps=time.steps, vars.to.plot = vars.to.plot)

```


```{r include=FALSE}

###################################################################################################
## Plot all variables current date

time.steps.4.plot = endDatePlotGlobal - as.Date("2020-03-01")
data.in <- la_data
vars.to.plot <- vars.plus.R

plot.all.variables.curr.date <- 
plot.model.data.all(traj.CI = traj.0, data.in = data.in, init.date.data = "2020-03-01", date.offset.4plot = 0, time.steps.4plot=time.steps.4.plot,
                    vars.to.plot=vars.plus.R)

# if (print.output==TRUE){
#   pdf(file = path(output.dir, "plot.all.variables.pdf"), width=10, height =10)
#   plot.all.variables.curr.date
#   dev.off()
# }
plot.all.variables.curr.date

```


# Epidemic model

<br>
<br>

## Tables: Parameter estimates {.tabset}

```{r include=FALSE}
###################################################################################################
## GET MODEL OUTPUT: summary

startDatePlot <- as.Date("2020-03-01")
endDatePlot <- endDatePlotGlobal
all_day_1s <- seq(startDatePlot,endDatePlot,by='month')
all_day_15s <- all_day_1s+14
date.in <- sort(c(all_day_1s,all_day_15s))
date.in <- date.in[1:(length(date.in)-1)]
tables.out <- get.PAR.tables(ABC_out=ABC_out, traj.CI=traj.0, date.in=date.in)
AKD_table = tables.out[[1]][,c(4:6)]

```

### $R(t)$, $r(t)$, $\alpha(t)$, $\kappa(t)$, $\delta(t)$, CFR(t), IFR(t)

```{r}

as.datatable(formattable(tables.out[[1]]), rownames = TRUE, options = list(pageLength = 10, autoWidth = TRUE))

if (print.output==TRUE) write.csv(tables.out[[1]], file = path(output.dir, "epi_model_output/PAR_table.csv"))
```

### CFR(t), IFR(t)

```{r}

as.datatable(formattable(tables.out[[4]]), rownames = TRUE, options = list(pageLength = 10, autoWidth = TRUE))

if (print.output==TRUE) write.csv(tables.out[[4]], file = path(output.dir, "epi_model_output/CFR_IFR_table.csv"))
```


## Prior and posterior parameter distributions {.tabset}

Plots for the prior distribution and estimated posterior distribution of each parameter at specific time intervals

```{r include=FALSE}
###################################################################################################
## PLOTTING DENSITIES

ABC.density <- ABC.par.out
ABC.density$Rt1 <- ABC.density$V1 * ABC.density$V2
ABC.density$Rt2 <- ABC.density$V1 * ABC.density$V9  # June-July 2020
ABC.density$Rt3 <- ABC.density$V1 * ABC.density$V14 # Nov-Dec 2020
ABC.density$Rt4 <- ABC.density$V1 * ABC.density$V14*1.2 # Dec.25.2020 -Jan.20.2021
ABC.density$Rt5 <- ABC.density$V1 * ABC.density$V14*.52 # Jan 20 - Feb 2021
ABC.density$Alpha4 <- ABC.density$V11 * 0.6
ABC.density$Kappa4 <- ABC.density$V12 * 0.75
ABC.density$Delta4 <- ABC.density$V10 * 1.5
##############################################################################################

ABC.density = ABC.density
## R0
PAR = "V1"
PAR.name = "R0"
PAR.mean = 3.65
PAR.sd = 0.1
R0_density <- plot_prior_posterior(ABC.density=ABC.density, PAR=PAR, PAR.name=PAR.name, PAR.mean=PAR.mean, PAR.sd=PAR.sd)
#R0_density

# Rt1_density
PAR = "Rt1"
PAR.name = "R(t) Apr-May, Aug-Oct 2020"
PAR.mean = 3.65*R0_redux1
PAR.sd = 0.1
Rt1_density <- plot_prior_posterior(ABC.density=ABC.density, PAR=PAR, PAR.name=PAR.name, PAR.mean=PAR.mean, PAR.sd=PAR.sd)
#Rt1_density

PAR = "Rt3"
PAR.name = "R(t) Nov-Dec 2020"
PAR.mean = 3.65*R0_redux3
PAR.sd = 0.1
Rt3_density <- plot_prior_posterior(ABC.density=ABC.density, PAR=PAR, PAR.name=PAR.name, PAR.mean=PAR.mean, PAR.sd=PAR.sd)
#Rt3_density

PAR = "V2"
PAR.name = "r(t) Mar-Apr 2020"
PAR.mean = 0.19
PAR.sd = 0.077
r1_density <- plot_prior_posterior(ABC.density=ABC.density, PAR=PAR, PAR.name=PAR.name, PAR.mean=PAR.mean, PAR.sd=PAR.sd)
#r1_density

PAR = "V13"
PAR.name = "r(t) May 2020 - Mar 2021"
PAR.mean = 0.475
PAR.sd = 0.09
r2_density <- plot_prior_posterior(ABC.density=ABC.density, PAR=PAR, PAR.name=PAR.name, PAR.mean=PAR.mean, PAR.sd=PAR.sd)
#r2_density

PAR = "V6"
PAR.name = "Alpha(t) March - April 2020"
PAR.mean = Alpha1
PAR.sd = 0.01
Alpha_density <- plot_prior_posterior(ABC.density=ABC.density, PAR=PAR, PAR.name=PAR.name, PAR.mean=PAR.mean, PAR.sd=PAR.sd)
#Alpha_density

PAR = "Alpha4"
PAR.name = "Alpha(t) Oct 2020 - Jan 2021"
PAR.mean = Alpha2*.7
PAR.sd = 0.01
Alpha4_density <- plot_prior_posterior(ABC.density=ABC.density, PAR=PAR, PAR.name=PAR.name, PAR.mean=PAR.mean, PAR.sd=PAR.sd)
#Alpha2_density

PAR = "Kappa4"
PAR.name = "Kappa(t) Oct 2020 - Jan 2021"
PAR.mean = Kappa2*.8
PAR.sd = 0.01
Kappa4_density <- plot_prior_posterior(ABC.density=ABC.density, PAR=PAR, PAR.name=PAR.name, PAR.mean=PAR.mean, PAR.sd=PAR.sd)
#Kappa4_density

PAR = "Delta4"
PAR.name = "Delta(t) Oct 2020 - Jan 2021"
PAR.mean = Delta2*1.5
PAR.sd = .01
Delta4_density <- plot_prior_posterior(ABC.density=ABC.density, PAR=PAR, PAR.name=PAR.name, PAR.mean=PAR.mean, PAR.sd=PAR.sd)
Delta4_density

PAR = "V7"
PAR.name = "Kappa(t) March - April 2020"
PAR.mean = Kappa1
PAR.sd = .01
Kappa_density <- plot_prior_posterior(ABC.density=ABC.density, PAR=PAR, PAR.name=PAR.name, PAR.mean=PAR.mean, PAR.sd=PAR.sd)
#Kappa_density

PAR = "V5"
PAR.name = "Delta(t) March - April 2020"
PAR.mean = Delta1
PAR.sd = .01
Delta_density <- plot_prior_posterior(ABC.density=ABC.density, PAR=PAR, PAR.name=PAR.name, PAR.mean=PAR.mean, PAR.sd=PAR.sd)
Delta_density

```

### $R(t)$

```{r}
R0_density
# Rt1_density
# Rt3_density

#if (print.output==TRUE){
  pdf(file = path(output.density.dir, "R0_density.pdf"), width=5, height =5)
  R0_density
  dev.off()
  
  # pdf(file = path(output.density.dir, "Rt1_density.pdf"), width=5, height =5)
  # Rt1_density
  # dev.off()
  # 
  # pdf(file = path(output.density.dir, "Rt3_density.pdf"), width=5, height =5)
  # Rt3_density
  # dev.off()
#}

```

### $r(t)$
```{r}
#r1_density
r2_density

#if (print.output==TRUE){
  # pdf(file = path(output.density.dir, "r1_density.pdf"), width=5, height =5)
  # r1_density
  # dev.off()
  
  pdf(file = path(output.density.dir, "r2_density.pdf"), width=5, height =5)
  r2_density
  dev.off()
#}

```


### $\alpha(t)$
```{r}
Alpha_density
#Alpha4_density

#if (print.output==TRUE){
  pdf(file = path(output.density.dir, "Alpha1_density.pdf"), width=5, height =5)
  Alpha_density
  dev.off()
  
  # pdf(file = path(output.density.dir, "Alpha4_density.pdf"), width=5, height =5)
  # Alpha4_density
  # dev.off()
#}

```


### $\kappa(t)$
```{r}
Kappa_density
#Kappa4_density

#if (print.output==TRUE){
  pdf(file = path(output.density.dir, "Kappa1_density.pdf"), width=5, height =5)
  Kappa_density
  dev.off()
  
  # pdf(file = path(output.density.dir, "Kappa4_density.pdf"), width=5, height =5)
  # Kappa4_density
  # dev.off()
#}

```


### $\delta(t)$
```{r}
Delta_density
#Delta4_density

#if (print.output==TRUE){
  pdf(file = path(output.density.dir, "Delta1_density.pdf"), width=5, height =5)
  Delta_density
  dev.off()
  
  # pdf(file = path(output.density.dir, "Delta4_density.pdf"), width=5, height =5)
  # Delta4_density
  # dev.off()
#}

```


{-}


## Figure: Model fits

Summarizes the epidemic model fit with COVID-19 data for LAC from March 1 through `r as.Date("2020-03-01") + no_obs -1` for all disease states across multiple views: New cases, representing new daily incidence; the current number in a compartment at a specific date, relevant for understanding current prevalence rates and comparing with healthcare capacity limitations; and cumulative counts until a specific date. Observed data for available compartments are plotted as black dots.

* **New = new daily incidence**
* **Current = current census in compartment** 
* **Cumulative = running total over time**
* Black dots depict COVID-19 data

```{r include=FALSE}

###################################################################################################
## Plot all variables faceted

time.steps.4.plot = endDatePlotGlobal - as.Date("2020-03-01") + 1
data.in <- la_data
vars.to.plot <- vars.plus.R

plot.all.variables <- 
plot.model.data.all(traj.CI = traj.0, data.in = data.in, init.date.data = "2020-03-01", date.offset.4plot = 15, time.steps.4plot=time.steps.4.plot,
                    vars.to.plot=vars.plus.R)

#if (print.output==TRUE){
  pdf(file = path(output.dir, "epi_model_output/plot.all.variables.pdf"), width=10, height =10)
  plot.all.variables
  dev.off()
#}

```

```{r}
plot.all.variables
```



## Figures: Time-Varying Parameters {.tabset}

```{r include=FALSE}

#endDatePlot <- as.Date("2020-12-01")
Fig3.plots <- plot.param.t(ABC_out = ABC_out, endDatePlot=endDatePlot)

R_t_plot = Fig3.plots[[1]]
R_t_eff_plot = Fig3.plots[[2]]
r_t_plot = Fig3.plots[[3]]
AKD_t_plot = Fig3.plots[[4]]

#if (print.output==TRUE){
  pdf(file = path(output.dir, "epi_model_output/plot_Rt.pdf"), width=5, height =5)
  R_t_plot
  dev.off()
  
  pdf(file = path(output.dir, "epi_model_output/plot_Rt_eff.pdf"), width=5, height =5)
  R_t_eff_plot
  dev.off()
  
  pdf(file = path(output.dir, "epi_model_output/plot_r_t.pdf"), width=5, height =5)
  r_t_plot
  dev.off()
  
  pdf(file = path(output.dir, "epi_model_output/plot_AKD_t.pdf"), width=5, height =5)
  AKD_t_plot
  dev.off()
#}

```

### Reproductive Number $R(t)$ and Effective Reproductive Number $Reff(t)$

```{r}
R_t_plot / R_t_eff_plot
```

### Fraction of Observed Infections $r(t)$

```{r}
r_t_plot
```

### $\alpha(t)$, $\kappa(t)$, $\delta(t)$

```{r}
AKD_t_plot
```

<!--CFR and IFR-->

```{r include=FALSE}

startDatePlot <- as.Date("2020-03-01")
all_day_1s <- seq(startDatePlot,endDatePlot,by='month')
all_day_15s <- all_day_1s+14
date.in <- sort(c(all_day_1s,all_day_15s))
CFR.IFR.plots.out <- CFR.IFR.plots(traj.CI=traj.0, date.in=date.in, endDatePlot = endDatePlot)
CFR_plot <- CFR.IFR.plots.out[[1]]
IFR_plot <- CFR.IFR.plots.out[[2]]

#if (print.output==TRUE){
  pdf(file = path(output.dir, "epi_model_output/CFR_plot.pdf"), width=5, height =5)
  CFR_plot
  dev.off()
  
  pdf(file = path(output.dir, "epi_model_output/IFR_plot.pdf"), width=5, height =5)
  IFR_plot
  dev.off()
#}

```

### Time-varying CFR(t)

```{r}
CFR_plot
```

### Time-varying IFR(t)
```{r}
IFR_plot
```


## Figures: Compartmental Variables {.tabset}

```{r include=FALSE}

time.steps.4.plot = endDatePlotGlobal - as.Date("2020-03-01") + 1
time.steps.4plot = time.steps.4.plot
data.in <- la_data
plot.annotations <- TRUE
plot.capacity <- TRUE
ymax=NULL

## Get compartmental variable plots TOGETHER and print/save
plot.out.H.I <- plot.out.compartmental(traj.CI = traj.CI, endDatePlot = endDatePlot)

#if (print.output==TRUE){
  pdf(file = path(output.dir, "epi_model_output/curr_infect_TOGETHER.pdf"),width=7, height = 7)
  plot.out.H.I[[2]]
  dev.off()
  
  pdf(file = path(output.dir, "epi_model_output/curr_healthcare_TOGETHER.pdf"), width=7, height = 7)
  plot.out.H.I[[1]]
  dev.off()
#}

## Get plots for individual variables (for ggplotly)

var.to.plot <- "I_detect_new"
#ymax=60000
plot.I.new <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)

var.to.plot <- "I"
#ymax=60000
plot.I <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)

var.to.plot <- "Itot"
#ymax=200000
plot.Itot <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)

var.to.plot <- "Itotcum"
#ymax=200000
plot.Itotcum <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)
ggplotly(plot.Itotcum)

var.to.plot <- "Htot"
#ymax = 3000
plot.Htot <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)

var.to.plot <- "Q"
#ymax = 3000
plot.Q <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)


var.to.plot <- "D_new"
#ymax = 200
plot.Dnew <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)

```

## Numbers infected {.tabset}

* **New = new daily incidence**
* **Current = current census in compartment** 
* **Cumulative = running total over time**
* Black dots depict COVID-19 data


### Current observed and total infections

```{r}
plot.out.H.I[[2]]
```


### New observed infections (with data)

```{r}
ggplotly(plot.I.new)

  pdf(file = path(output.dir, "epi_model_output/Inew.pdf"), width=5, height =5)
  plot.I.new
  dev.off()

```


### Current estimated total infections

```{r width=3}
ggplotly(plot.Itot)
```

### Current observed infections

```{r}
ggplotly(plot.I)
```

### Current observed and total infections (together)

```{r}
plot.out.H.I[[2]]
```

{-}

## Numbers in healthcare {.tabset}

* **New = new daily incidence**
* **Current = current census in compartment** 
* **Cumulative = running total over time**
* Black dots depict COVID-19 data
* Dotted black line marks healthcare capacity limits

### Current in hospital and in ICU

```{r}
plot.out.H.I[[1]]
```

### New deaths

```{r}
ggplotly(plot.Dnew)

#if (print.output==TRUE){
  pdf(file = path(output.dir, "epi_model_output/Dnew.pdf"), width=5, height =5)
  plot.Dnew
  dev.off()
#}

```

### Current in hospital

```{r}
ggplotly(plot.Htot)
```

### Current in ICU

```{r}
ggplotly(plot.Q)
```

{-}



# Risk model

<!--- 
Read in input data
--->

```{r include=FALSE}
###############################################################################################################
###############################################################################################################
## Read in conditional log(RR) for (H|I), (V|H), (D|V), for each risk profile q, calculated by the JAM model
## Data coming from: Guan et al. 2020, Petrilli et al. 2020
psi.mat <- read.csv(path(data.dir, "risk_model_2021/psi.mat.csv"), sep=",", header=TRUE,row.names = 1)

# psi.mat["age_80.",] <- rep(2.75,times=3) # c(1,.5,1)
# psi.mat["age_65.79",] <- rep(1.8, times=3)
# psi.mat["age_50.64",] <- rep(.85, times=3)

psi.mat["age_80.",] <- rep(2.9,times=3) # c(1,.5,1)
psi.mat["age_65.79",] <- rep(1.9, times=3)
psi.mat["age_50.64",] <- rep(.95, times=3)

###############################################################################################################
## Get profile matrix X.mat
X.mat <- read.csv(path(data.dir, "risk_model_2021/X.mat.csv"), sep=",", header=TRUE,row.names = 1)
rownames(X.mat) <- c(1:nrow(X.mat))
n_factors <- ncol(X.mat)
n_profiles <- nrow(X.mat)

#########################################################################################################
## Read in correlation structure, $\Sigma$, between the risk factors p
## Correlation structure is weighted according to the prevalence of each race/ethnicity in LA County
## Calculated using data coming from: The National Health and Nutrition Examination Survey (NHANES)
SIGMA <- read.csv(path(data.dir, "risk_model_2021/SIGMA.csv"), sep=",", header=TRUE,row.names = 1)

#########################################################################################################
## Prevalence of each risk factor p in the population for LA County
## Data coming from:
# [Los Angeles County Health Survey](http://www.publichealth.lacounty.gov/ha/hasurveyintro.htm)
# [California Health Information Survey](http://ask.chis.ucla.edu)
# American Community Survey (via "tidycensus" R package)
pop.prev.2021 <- read.csv(path(data.dir, "risk_model_2021/Pop.prevalence.2021.csv"), sep=",", header=TRUE,row.names = 1) %>% as.data.frame()

```

## $\psi$ matrix - log conditional risks {.tabset}

### $\psi$ matrix edited

```{r}
formattable(psi.mat)
```


<!---
Calculate prevalence of each profile in overall LAC population
--->

```{r riskprofiles, include=FALSE, eval=TRUE}

# calc_profile_prev<- path(code.risk.dir, "calc_profile_prev_2021.R")
# source(calc_profile_prev)

## Reading this in rather than sourcing due to long runtime
profile.cnt.freq <- read.csv(path(data.dir, "risk_model_2021/profile.cnt.freq.csv"), sep=",", header=TRUE,row.names = 1)
rownames(profile.cnt.freq) <- c(1:nrow(profile.cnt.freq))

## Extracting only the frequencies
freq.PREV.q <- as.vector(profile.cnt.freq[,1])
freq.PREV.q[34] <- 0.02981
freq.PREV.q[10] <- 0.02839

```


<!---
Estimate risk probabilities with baseline from epidemic model
--->

```{r estimate-risk-integrated}

##################################################
## INPUTS: EPIDEMIC MODEL
## Get mean estimates of Alpha(t), Kappa(t), Delta(t) over time 
table1 <- AKD_table
for (i in 1:nrow(table1)){  table1[i,] <- AKD_table[i,] %>% mutate_if(is.character, function(x) unlist(strsplit(x, " "))[1])}
table1 <- as.data.frame(apply(table1, 2, as.numeric)) 
#rownames(table1) <- rownames(AKD_table)
table1$dates <- as.Date(rownames(AKD_table))

##################################################
## INPUTS: TIMES
### Chosen times to run analysis at
t1 <- "2020-05-15"
t2 <- "2020-08-01"
t3 <- "2020-10-15"
t4 <- "2020-11-15"
t5 <- "2020-12-15"
t6 <- "2021-01-15"
t7 <- "2021-02-15"
t8 <- "2021-03-01"

times.dates <- as.Date(c(t1,t2,t3,t4,t5,t6,t7,t8))
n.times <- length(times.dates)

### Get Alpha Kappa Delta means at dates
risk.probs.POSTERIORS <- table1 %>% filter(dates %in% times.dates)
risk.probs.POSTERIORS$dates <- NULL

##################################################
## INPUTS: OBSERVED LAC DATA ON ILLNESSES
### Observed LAC age prevalence in (I) infections

# 
# # n.dates.LAC.obs.age <- length(times)
# # freq.LAC.obs.age <- matrix(nrow=3, ncol=n.dates.LAC.obs.age)
# # colnames(freq.LAC.obs.age) <- times
# # rownames(freq.LAC.obs.age) <- c("Age0.19","Age20.64","Age65.")
# # # freq.LAC.obs.age[,1] <- c(0.011, 0.750, 0.239)  # Apr15
# # # freq.LAC.obs.age[,2] <- c(0.080, 0.799, 0.121)  # Jul15
# # # freq.LAC.obs.age[,3] <- c(0.102, 0.784, 0.114)  # Oct15
# # # freq.LAC.obs.age[,1] <- c(0.035, 0.749, 0.216)  # May15
# # # freq.LAC.obs.age[,2] <- c(0.080, 0.799, 0.121)  # Jul15
# # # freq.LAC.obs.age[,3] <- c(0.099, 0.785, 0.116)  # Sep15
# # # freq.LAC.obs.age[,4] <- c(0.102, 0.784, 0.114)  # Oct15
# # freq.LAC.obs.age[,1] <- c(0.035, 0.749, 0.216)  # May.15
# # freq.LAC.obs.age[,2] <- c(0.089, 0.791, 0.120)  # Aug.1
# # freq.LAC.obs.age[,3] <- c(0.102, 0.784, 0.114)  # Oct.15

## Readin CA state age data 
ages_pct <- latimes_age_readin()

## Find closest dates in the CA state age data to our selected dates
closest.dates <- times.dates
for (i in 1:n.times){
  x=times.dates[i]
  closest.dates[i] <- (ages_pct[which(abs(ages_pct$date - x) == min(abs(ages_pct$date - x))),"date"])
}
## Select age data at closest to selected dates and put into correct format
freq.obs.age <- ages_pct %>% filter(date %in% closest.dates) %>% select(date,case_pct,age.strata) #%>% unique()
freq.LAC.obs.age <- spread(freq.obs.age, age.strata, case_pct)

##################################################
## APPLY CODE TO GET ESTIMATE RISK PROBABILITIES WITH BASELINE FROM EPIDEMIC MODEL
calc_integrated_risk_model<- path(code.risk.dir, "integrated_risk_model.R")
source(calc_integrated_risk_model)

Pr.freq.FUN.out <- Pr.freq.FUN(X.mat=X.mat, 
                               freq.PREV.q=freq.PREV.q,
                            freq.LAC.obs.age=freq.LAC.obs.age,
                            risk.probs.POSTERIORS=risk.probs.POSTERIORS,
                            psi.mat=psi.mat)
### OUTPUTS
Pr.OUT <- Pr.freq.FUN.out[[1]]
freq.OUT <- Pr.freq.FUN.out[[2]]   

```


<!---
Plot mean (min,max) of each probability over profiles within each age group
--->

```{r}

AGE.min.max.Pr.plot<- path(code.risk.dir, "AGE.min.max.Pr.plot.R")
source(AGE.min.max.Pr.plot)

```

## Risk probabilities by age {.tabset}

Figures show the mean, minimum, and maximum values of the probabilities of severe illness for each age group. The minimum and maximum indicate the range of values that can be taken on by the sub-profiles within each age group; for example for age group 65-79, a profile with low BMI, no smoking, and no comorbidities will have lower probabilites of severe illness than a profile with high BMI, smoking, and comorbidities.

### P(H|I)

Probability of hospitalization given infection

```{r}

#if (print.output==TRUE){
  pdf(file = path(output.dir, "risk_model_output/plot.HI.AGES.pdf"), width=5, height =5)
  plot.HI.AGES
  dev.off()
#}

plot.HI.AGES
```


### P(Q|H)

Probability of ICU admission given hospitalization

```{r}

#if (print.output==TRUE){
  pdf(file = path(output.dir, "risk_model_output/plot.QH.AGES.pdf"), width=5, height =5)
  plot.QH.AGES
  dev.off()
#}

plot.QH.AGES
```


### P(D|Q)

Probability of death given ICU admission

```{r}

#if (print.output==TRUE){
  pdf(file = path(output.dir, "risk_model_output/plot.DQ.AGES.pdf"), width=5, height =5)
  plot.DQ.AGES
  dev.off()
#}

plot.DQ.AGES
```


### P(D|I)

Probability of death given infection

```{r}

#if (print.output==TRUE){
  pdf(file = path(output.dir, "risk_model_output/plot.DI.AGES.pdf"), width=5, height =5)
  plot.DI.AGES
  dev.off()
#}

plot.DI.AGES
```


## Risk probability tables {.tabset}

<!---
First clean the data and get necessary functions for extracting tables
--->

```{r}
clean_data_risk_2021 <- path(code.risk.dir, "clean_data_risk_2021.R")
source(clean_data_risk_2021)
```

<!---
Then get the probability by profile tables
--->

```{r}
Pr.HI <- extract.Pr.table(n.times=n.times,order.pr = 1)
Pr.QH <- extract.Pr.table(n.times=n.times,order.pr = 2)
Pr.DQ <- extract.Pr.table(n.times=n.times,order.pr = 3)
Pr.DI <- extract.Pr.table(n.times=n.times,order.pr = 4)

if (print.output==TRUE) {
  write.csv(Pr.HI, file = path(output.dir, "risk_model_output/Pr.tables/Pr.HI.csv"))
  write.csv(Pr.QH, file = path(output.dir, "risk_model_output/Pr.tables/Pr.QH.csv"))
  write.csv(Pr.DQ, file = path(output.dir, "risk_model_output/Pr.tables/Pr.DQ.csv"))
  write.csv(Pr.DI, file = path(output.dir, "risk_model_output/Pr.tables/Pr.DI.csv"))
}

```

### P(H|I)

Probability of hospitalization given infection

```{r}
as.datatable(formattable(Pr.HI), rownames = TRUE, options = list(pageLength = 10, autoWidth = TRUE))
```

### P(Q|H)

Probability of ICU admission given hospitalization

```{r}
as.datatable(formattable(Pr.QH), rownames = TRUE, options = list(pageLength = 10, autoWidth = TRUE))
```

### P(D|Q)

Probability of death given ICU admission

```{r}
as.datatable(formattable(Pr.DQ), rownames = TRUE, options = list(pageLength = 10, autoWidth = TRUE))

```

### P(D|I)

Probability of death given infection

```{r}

as.datatable(formattable(Pr.DI), rownames = TRUE, options = list(pageLength = 10, autoWidth = TRUE))

```


<!---
Get CFR and IFR by profile
--->

```{r}

get_CFR_IFR_2021 <- path(code.risk.dir, "get_CFR_IFR_2021.R")
source(get_CFR_IFR_2021)

CFR.IFR.profiles <- get.CFR.IFR.profiles(ABC.out.mat=ABC.out.mat, time.steps=time.steps, iter=iter, data.prev=data.prev, times.dates=times.dates, round.by=5)

CFR.OUT <- CFR.IFR.profiles[[1]]
IFR.OUT <- CFR.IFR.profiles[[2]]

```

<!---
Plot CFR and IFR by age
--->

## CFR and IFR by age {.tabset}

CFR: Case fatality rate (observed deaths / observed infections)

IFR: Infection fatality rate (observed deaths / estimated total infections)

Figures show the mean, minimum, and maximum of the mean values of the CFR and IFR for each age group. The minimum and maximum indicate the range of values that can be taken on by the sub-profiles within each age group; for example for age group 65-79, a profile with low BMI, no smoking, and no comorbidities will have a lower CFR and IFR than a profile with high BMI, smoking, and comorbidities.

```{r}
AGE.min.max.CFR.IFR.plot <- path(code.risk.dir, "AGE.min.max.CFR.IFR.plot.R")
source(AGE.min.max.CFR.IFR.plot)

plot.CFR.AGES = plot.CFR.IFR.ages(is.CFR=1, CFR.OUT=CFR.OUT, freq.OUT=freq.OUT, X.mat=X.mat)
plot.IFR.AGES = plot.CFR.IFR.ages(is.CFR=0, CFR.OUT=IFR.OUT, freq.OUT=freq.OUT, X.mat=X.mat)


#if (print.output==TRUE){
  pdf(file = path(output.dir, "risk_model_output/plot.CFR.AGES.pdf"), width=5, height =5)
  plot.CFR.AGES
  dev.off()
#}
  
#if (print.output==TRUE){
  pdf(file = path(output.dir, "risk_model_output/plot.IFR.AGES.pdf"), width=5, height =5)
  plot.IFR.AGES
  dev.off()
#}  



```

### CFR

```{r}
plot.CFR.AGES
```

### IFR

```{r}
plot.IFR.AGES
```


## CFR and IFR: populous profiles {.tabset}

Here we plot, for the single most populous profiles in each age group, the mean CFR and IFR and its 95% confidence interval 

```{r}

AGE.choose.profiles.CFR.IFR.plot <- path(code.risk.dir, "AGE.choose.profiles.CFR.IFR.plot.R")
source(AGE.choose.profiles.CFR.IFR.plot)

plot.CFR.choose = CFR.choose.profile.plot(is.CFR=1, Profile=Profile, freq.PREV.q=freq.PREV.q, CFR.OUT=CFR.OUT)
plot.IFR.choose = CFR.choose.profile.plot(is.CFR=0, Profile=Profile, freq.PREV.q=freq.PREV.q, CFR.OUT=IFR.OUT)

#if (print.output==TRUE){
  pdf(file = path(output.dir, "risk_model_output/plot.CFR.choose.pdf"), width=7, height =7)
  plot.CFR.choose
  dev.off()
#}
  
#if (print.output==TRUE){
  pdf(file = path(output.dir, "risk_model_output/plot.IFR.choose.pdf"),  width=7, height =7)
  plot.IFR.choose
  dev.off()
#}  


```

### CFR

```{r}
plot.CFR.choose
```

### IFR

```{r}
plot.IFR.choose
```



## CFR and IFR tables{.tabset}

CFR and IFR tables for all profiles

```{r}

CFR.CI.table <- get.CFR.CI.table(n.times=n.times, CFR.OUT=CFR.OUT, data.FULL=data.FULL)
IFR.CI.table <- get.CFR.CI.table(n.times=n.times, CFR.OUT=IFR.OUT, data.FULL=data.FULL)

#if (print.output==TRUE) {
  write.csv(CFR.CI.table, file = path(output.dir, "risk_model_output/CFR.tables/CFR.csv"))
  write.csv(IFR.CI.table, file = path(output.dir, "risk_model_output/CFR.tables/IFR.csv"))
#}

```

### CFR

Case fatality rate (observed deaths / observed infections)

```{r}
as.datatable(formattable(CFR.CI.table), rownames = TRUE, options = list(pageLength = 10, autoWidth = TRUE))
```

### IFR

Infection fatality rate (observed deaths / estimated total infections)

```{r}
as.datatable(formattable(IFR.CI.table), rownames = TRUE, options = list(pageLength = 10, autoWidth = TRUE))
```


<!---
Calculate frequency of risk factor groups by stage of disease
Create plots for each risk factor group
--->

```{r get-group-by-stage}

## Source code to get function to get plot comparing age in deaths for data and model predictions
AGE.D.data.model <- path(code.risk.dir, "AGE.D.data.model.R")
source(AGE.D.data.model)

plot.D.age <- plot.freq.age.D(freq.age.D=freq.age.D)
 
  pdf(file = path(output.dir, "risk_model_output/plot.D.age.pdf"),width=5, height =5)
  plot.D.age
  dev.off()


## Source code to clean data and get function for creating "Stage of disease by risk factor group" figures
grouped_fig_code <- path(code.risk.dir, "clean_data_grouped_figs.R")
source(grouped_fig_code)

## Get "Stage of disease by risk factor group" figures
var = "Age"
var.name <- "Age"
p.prev.age.stage.DATES <- grouped.var.figs(full.data=full.data, var=var, var.name=var.name, times.dates=times.dates)

  pdf(file = path(output.dir, "risk_model_output/p.prev.age.stage.DATES.pdf"), width=5, height =5)
  p.prev.age.stage.DATES
  dev.off()

var = "BMI"
var.name <- "Obesity"
p.prev.BMI.stage.DATES <- grouped.var.figs(full.data=full.data, var=var, var.name=var.name, times.dates=times.dates)

var = "Comorbidity"
var.name = "Comorbidity"
p.prev.comorbidity.stage.DATES <- grouped.var.figs(full.data=full.data, var=var, var.name=var.name, times.dates=times.dates)

var = "Smoker"
var.name = "Smoking status"
p.prev.smoking.stage.DATES <- grouped.var.figs(full.data=full.data, var=var, var.name=var.name, times.dates=times.dates)

```


## Stage of disease by risk factor group {.tabset}

Estimated frequency of groups in the overall LAC population, and the population of individuals in each stage of disease from infected, hospitalized, admitted to ICU, to deceased on each date `times.dates`: (A) Risk Groups, (B) age group, (C) obesity class groups, (D) any comorbidity group, and (E) smoking status group. 

### Deaths: data and model predictions

```{r}
plot.D.age

```


### Age

```{r}
p.prev.age.stage.DATES
```

### Cormorbidity

```{r}
p.prev.comorbidity.stage.DATES
```

### BMI

```{r}
p.prev.BMI.stage.DATES
```

### Smoking status

```{r}
p.prev.smoking.stage.DATES
```

{-}
